[Artifact Presentation] Damegender: \\ Writing and Comparing Gender Detection Tools

### 2020-05-15 paper2sattose.tex
paper2sattose.tex: start fixes about accents

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolceurws}
\usepackage{xcolor}
\usepackage{url}

@@

\author{
David Arroyo Menendez, Jesus Gonzalez-Barahona \\ Grupo de Sistemas y Comunicaciones (GSyC) \\ Universidad Rey Juan Carlos, Madrid, Spain \\ \{d.arroyome@alumnos, jgb@gsyc\}.urjc.es
}

@@

Thanks to:
Gregorio Robles by the support and suggestions for publish this article in Sattose

@@

Jesus Gonzalez Boticario and the people who is working with him in the UNED by the motivation towards the machine learning.

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{twocolceurws}
\usepackage{xcolor}
\usepackage{url}

@@

\author{
David Arroyo Menéndez, Jesus González-Barahona, Gregorio Robles \\ Grupo de Sistemas y Comunicaciones (GSyC) \\ Universidad Rey Juan Carlos, Madrid, Spain \\ \{d.arroyome@alumnos, jgb@gsyc, grex@gsyc\}.urjc.es
}

@@

Thanks to:

@@

Jesus González Boticario and the people who is working with him in the UNED by the motivation towards the machine learning.

All people working with Jesus González Barahona and Gregorio Robles.
